---
title: "House Price by States"
author: "TH"
date: "March 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Collect data
The data are from two sources:
1. Home prices by state is from trulia (https://www.trulia.com/home_prices/)
2. State Area Measurements and Internal Point Coordinates is from (https://www.census.gov/geo/reference/state-area.html)


## Visualize data using leaflet
Home price by state plot is created using leaflet, and radius of each circle is proportional to listing price.
```{r, warning=FALSE}
library(leaflet)
setwd('D:/Dropbox/E-books/_Coursera/9_Developing_Data_Products/Week2')
housing_df <- read.csv('house_listing_price.csv', header = TRUE, stringsAsFactors = FALSE)
head(housing_df)

my_map <- housing_df %>%
    leaflet() %>%
    addTiles() %>%
    addCircles(lat=housing_df$Lat, lng=housing_df$Long, 
              weight = 1, radius = (housing_df$Average.Listing.Price)/2, 
              popup = strwrap(housing_df$Average.Listing.Price))
my_map
```

